Experiences with long-term monitoring of a large-scale distributed and heterogenous cyberinfrastructure

### 2013-01-06 pubs/papers/inca-analysis/Inca-anaylsis.tex
Minor updates to title.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15049 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
Added fg- machine paritition table info.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15055 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\title{}

\numberofauthors{1}

\author{
\alignauthor
Shava Smallen, Sameer Tilak, etc. \\
\affaddr{University of California, San Diego} \\ 
\affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
\email{\{ssmallen,sameer\}@sdsc.edu}\\
}

@@

\section{Future Grid Overview} (1 page)
Add description of load -- vm count, hrs. etc.

@@

>>>>

\title{Experiences with long-term monitoring of a large-scale distributed and heterogenous cyberinfrastructure}

\author{\IEEEauthorblockN{Shava Smallen and Sameer Tilak}
\IEEEauthorblockA{ University of California, San Diego \\
La Jolla, CA, USA, Email: {\{ssmallen,stilak\}}@ucsd.edu}
}

@@

\section{FutureGrid Overview} (1 page)
Add description of load -- vm count, hrs. etc.

@@

\begin{table*}

\begin{tabular}{| l | c | c | c | c | }
 \hline
Resource & HPC  & Eucalyptus & Nimbus  & Openstack   \\
  \hline
Site 1 resource 1 (1136 cores) & 44.7\% (508 cores) & 21.1\% (240 cores) & &  19.7\% (224 cores) \\  \hline
Site1 resource 2(664 cores) & 100\% (664 cores) & & & \\  \hline
Site 2 (705.28 cores) & 86.2\% (608 cores) & & 13.8\% (97.28 cores) &  \\  \hline
Site 3 (640 cores) & 48.8\% (312 cores) & & 51.2\% (328 cores) &  \\  \hline
Site 4 (632 cores) & 43\% (272 cores) & 15.2\% (96 cores) & 22.8\% (144 cores) & 3.8\% (24 cores)   \\  \hline
Site 5 (192 cores) & & & 95.8\% (184 cores) &   \\  \hline

\end{tabular}
\caption{FutureGrid: Machine Partition Information (A small percentage of nodes may be unavailable or used for management) }
 \label{tab:fg-machine-allocation}

\end{table*}
